---
title: "MS Data Analysis - Flu Project"
author: "Isabel Uribe"
date: "2023-11-09"
output: html_document
---

Read in tidy tsv file for flu sites.
```{r}
library(readr)
library(tidyverse) ## for data wrangling
library(ggplot2) ##data plotting
library(viridis) ##color palettes
library(svglite) ##save plots as svg

pR_sites_FLU = read_tsv("tidy_sites_Isabel.tsv", show_col_types = FALSE) %>%
  filter(Organism != "Human") %>%
  filter(Best_Localization >= 0.9)
```

Look at distribution of sites across amino acids (can filter score here).
```{r}
amino.acids_FLU = pR_sites_FLU %>%
  filter(Score >= 4) %>%
  group_by(Condition, Modified_Residue, Index) %>%
  distinct(Index) 
amino.acids_FLU = amino.acids_FLU %>%
  group_by(Condition, Modified_Residue) %>%
  count(Modified_Residue)

write_tsv(amino.acids_FLU, "mod_AA_isabel_flu.tsv")
```

Create heat map to see number of modifications on flu proteins (can filter score here).
```{r}
number_sites = pR_sites_FLU %>%
  filter(Score >= 4) %>%
  group_by(Condition, Protein_Name) %>% 
  distinct(Protein_Index) %>%
  count()

colnames(number_sites) = c("Condition", "Protein_Name", "Number_of_Sites")

sites_list = c(1, 5, 10, 15, 20)

x = ggplot(data = number_sites, mapping = aes(x = Condition, 
                                              y = Protein_Name, 
                                              fill = Number_of_Sites)) +
geom_tile() +
  theme_classic() +
  xlab(label = "Condition") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
        axis.text.y = element_text(size = 20),
        plot.title = element_text(hjust = 0.5, size = 35),
        axis.title = element_text(size = 25),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15)) +
  scale_fill_viridis(name = "Number of Sites", breaks = sites_list, labels = c("1", "5", "10", "15", "20"), direction = -1, option = "D") +
  ggtitle(label = "Sites on Flu Proteins") 
   
ggsave("isabel_number_of_sites_flu_proteins.svg", x, width = 30, height = 20, units = "cm")
```

Create heat map to see abundance of modifications on flu proteins.
```{r}
library(svglite)
abundance_est = pR_sites_FLU %>%
  filter(Mod_Class == "pep_one-mod") %>%
  filter(Score >= 4) %>%
  group_by(Condition, Protein_Name) %>% 
  summarise(sum(Total_PSMs))

ab_est = as.data.frame(abundance_est)
colnames(ab_est) = c("Condition", "Protein_Name", "Total_PSMs_for_Protein")

test = ab_est %>%
  group_by(Condition) %>%
  summarise(max(Total_PSMs_for_Protein))

psm_list = c(1, 100, 200, 300, 400, 500, 600, 700, 800)


x = ggplot(data = ab_est, mapping = aes(x = Condition, y = Protein_Name, fill = Total_PSMs_for_Protein)) +
geom_tile() +
  theme_classic() +
  xlab(label = "Condition") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
        axis.text.y = element_text(size = 20),
        plot.title = element_text(hjust = 0.5, size = 35),
        axis.title = element_text(size = 25),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15)) +
  scale_fill_viridis(name = "Total PSMs", breaks = psm_list, labels = c("1", "100", "200", "300", "400", "500", "600", "700", "800"), direction = -1, option = "D") +
  ggtitle(label = "Abundance of Sites on Flu Proteins") 

ggsave("isabel_site_abundance_flu_proteins.svg", x, width = 30, height = 20, units = "cm")
```

Create heat map to see presence or absence of Indices on NS1.
```{r}
map_of_NS1 = pR_sites_FLU %>%
  filter(Protein_Name == "Non-structural_protein_1") %>%
  filter(Score >= 4) %>%
  group_by(Condition, Protein_Index) %>%
  summarise(max(Score))

colnames(map_of_NS1) = c("Condition", "Index", "Site_Score")

score_list = c(2, 3, 4, 5, 6, 7, 9)

x = ggplot(data = map_of_NS1, mapping = aes(x = Condition, 
                                              y = Index, 
                                              fill = Site_Score)) +
geom_tile() +
  theme_classic() +
  xlab(label = "Condition") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
        axis.text.y = element_text(size = 20),
        plot.title = element_text(hjust = 0.5, size = 35),
        axis.title = element_text(size = 25),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15)) +
  scale_fill_viridis(name = "Max Site Score", breaks = score_list, labels = c("2", "3", "4", "5", "6", "7", "9"), direction = -1, option = "D") +
  ggtitle(label = "Sites on Non-structural Protein 1") 
  
ggsave("isabel_NS1_sites.svg", x, width = 30, height = 20, units = "cm")
```

Create heat map to see presence or absence of Indices on NP.
```{r}
map_of_NP = pR_sites_FLU %>%
  filter(Protein_Name == "Nucleoprotein") %>%
  filter(Score >= 4) %>%
  group_by(Condition, Protein_Index) %>%
  summarise(max(Score))

colnames(map_of_NP) = c("Condition", "Index", "Site_Score")

score_list = c(2, 3, 4, 5, 6, 7, 9)

x = ggplot(data = map_of_NP, mapping = aes(x = Condition, 
                                              y = Index, 
                                              fill = Site_Score)) +
geom_tile() +
  theme_classic() +
  xlab(label = "Condition") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
        axis.text.y = element_text(size = 20),
        plot.title = element_text(hjust = 0.5, size = 35),
        axis.title = element_text(size = 25),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15)) +
  scale_fill_viridis(name = "Max Site Score", breaks = score_list, labels = c("2", "3", "4", "5", "6", "7", "9"), direction = -1, option = "D") +
  ggtitle(label = "Sites on Nucleoprotein") 

ggsave("isabel_NP_sites.svg", x, width = 30, height = 25, units = "cm")
```

Create heat map to see presence or absence of Indices on Matrix Protein 1.
```{r}
map_of_M1 = pR_sites_FLU %>%
  filter(Protein_Name == "Matrix_protein_1") %>%
  filter(Score >= 4) %>%
  group_by(Condition, Protein_Index) %>%
  summarise(max(Score))

colnames(map_of_M1) = c("Condition", "Index", "Site_Score")

score_list = c(2, 3, 4, 5, 6, 7, 9)

x = ggplot(data = map_of_M1, mapping = aes(x = Condition, 
                                              y = Index, 
                                              fill = Site_Score)) +
geom_tile() +
  theme_classic() +
  xlab(label = "Condition") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
        axis.text.y = element_text(size = 20),
        plot.title = element_text(hjust = 0.5, size = 35),
        axis.title = element_text(size = 25),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15)) +
  scale_fill_viridis(name = "Max Site Score", breaks = score_list, labels = c("2", "3", "4", "5", "6", "7", "9"), direction = -1, option = "D") + 
  ggtitle(label = "Sites on Matrix Protein 1") 
  
ggsave("isabel_M1_sites.svg", x, width = 30, height = 30, units = "cm")
```

Create heat map to see presence or absence of Indices on Hemagglutinin.
```{r}
map_of_HA = pR_sites_FLU %>%
  filter(Protein_Name == "Hemagglutinin") %>%
  filter(Score >= 4) %>%
  group_by(Condition, Protein_Index) %>%
  summarise(max(Score))

colnames(map_of_HA) = c("Condition", "Index", "Site_Score")

score_list = c(2, 3, 4, 5, 6, 7, 9)

x = ggplot(data = map_of_HA, mapping = aes(x = Condition, 
                                              y = Index, 
                                              fill = Site_Score)) +
geom_tile() +
  theme_classic() +
  xlab(label = "Condition") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
        axis.text.y = element_text(size = 20),
        plot.title = element_text(hjust = 0.5, size = 35),
        axis.title = element_text(size = 25),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15)) +
  scale_fill_viridis(name = "Max Site Score", breaks = score_list, labels = c("2", "3", "4", "5", "6", "7", "9"), direction = -1, option = "D") +
  ggtitle(label = "Sites on Hemagglutinin") 

ggsave("isabel_HA_sites.svg", x, width = 30, height = 25, units = "cm")
```

Create heat map to see presence or absence of Indices on Neuraminidase.
```{r}
map_of_NA = pR_sites_FLU %>%
  filter(Protein_Name == "Neuraminidase") %>%
  filter(Score >= 4) %>%
  group_by(Condition, Protein_Index) %>%
  summarise(max(Score))

colnames(map_of_NA) = c("Condition", "Index", "Site_Score")

score_list = c(2, 3, 4, 5, 6, 7, 9)

x = ggplot(data = map_of_NA, mapping = aes(x = Condition, 
                                              y = Index, 
                                              fill = Site_Score)) +
geom_tile() +
  theme_classic() +
  xlab(label = "Condition") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
        axis.text.y = element_text(size = 20),
        plot.title = element_text(hjust = 0.5, size = 35),
        axis.title = element_text(size = 25),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15)) +
  scale_fill_viridis(name = "Max Site Score", breaks = score_list, labels = c("2", "3", "4", "5", "6", "7", "9"), direction = -1, option = "D") +
  ggtitle(label = "Sites on Neuraminidase") 

ggsave("isabel_NA_sites.svg", x, width = 30, height = 25, units = "cm")
```

Create heat map to see presence or absence of Indices on Polymerase Basic Protein 2.
```{r}
map_of_PB2 = pR_sites_FLU %>%
  filter(Protein_Name == "Polymerase_basic_protein_2") %>%
  filter(Score >= 4) %>%
  group_by(Condition, Protein_Index) %>%
  summarise(max(Score))

colnames(map_of_PB2) = c("Condition", "Index", "Site_Score")

score_list = c(2, 3, 4, 5, 6, 7, 9)

x = ggplot(data = map_of_PB2, mapping = aes(x = Condition, 
                                              y = Index, 
                                              fill = Site_Score)) +
geom_tile() +
  theme_classic() +
  xlab(label = "Condition") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
        axis.text.y = element_text(size = 20),
        plot.title = element_text(hjust = 0.5, size = 35),
        axis.title = element_text(size = 25),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15)) +
  scale_fill_viridis(name = "Max Site Score", breaks = score_list, labels = c("2", "3", "4", "5", "6", "7", "9"), direction = -1, option = "D") +
  ggtitle(label = "Sites on Polymerase Basic Protein 2") 

ggsave("isabel_PB2_sites.svg", x, width = 30, height = 15, units = "cm")
```

Create heat map to see presence or absence of Indices on PB1.
```{r}
map_of_PB1 = pR_sites_FLU %>%
  filter(Protein_Name == "Polymerase_basic_protein_1") %>%
  filter(Score >= 4) %>%
  group_by(Condition, Protein_Index) %>%
  summarise(max(Score))

colnames(map_of_PB1) = c("Condition", "Index", "Site_Score")

score_list = c(2, 3, 4, 5, 6, 7, 9)

x = ggplot(data = map_of_PB1, mapping = aes(x = Condition, 
                                              y = Index, 
                                              fill = Site_Score)) +
geom_tile() +
  theme_classic() +
  xlab(label = "Condition") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
        axis.text.y = element_text(size = 20),
        plot.title = element_text(hjust = 0.7, size = 35),
        axis.title = element_text(size = 25),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15)) +
  scale_fill_viridis(name = "Max Site Score", breaks = score_list, labels = c("2", "3", "4", "5", "6", "7", "9"), direction = -1, option = "D") +
  ggtitle(label = "Sites on Polymerase Basic Protein 1") 

ggsave("isabel_PB1_sites.svg", x, width = 30, height = 20, units = "cm")
```
Create heat map to see presence or absence of Indices on PA.
```{r}
# map_of_PA = pR_sites_FLU %>%
#   filter(Protein_Name == "Polymerase_acidic_protein") %>%
#   filter(Score >= 4) %>%
#   group_by(Condition, Protein_Index) %>%
#   summarise(max(Score))
# 
# colnames(map_of_PA) = c("Condition", "Index", "Site_Score")
# 
# score_list = c(2, 3, 4, 5, 6, 7, 9)
# 
# x = ggplot(data = map_of_PA, mapping = aes(x = Condition,
#                                               y = Index,
#                                               fill = Site_Score)) +
# geom_tile() +
#   theme_classic() +
#   xlab(label = "Condition") +
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
#         axis.text.y = element_text(size = 20),
#         plot.title = element_text(hjust = 0.7, size = 35),
#         axis.title = element_text(size = 25),
#         legend.title = element_text(size = 20),
#         legend.text = element_text(size = 15)) +
#   scale_fill_viridis(name = "Max Site Score", breaks = score_list, labels = c("2", "3", "4", "5", "6", "7", "9"), direction = -1, option = "D") +
#   ggtitle(label = "Sites on Polymerase Acidic Protein")
# 
# ggsave("isabel_PA_sites.svg", x, width = 30, height = 20, units = "cm")
```

Create heat map to see presence or absence of Indices on NEP.
```{r}
# map_of_NEP = pR_sites_FLU %>%
#   filter(Protein_Name == "Nuclear_export_protein") %>%
#   filter(Score >= 4) %>%
#   group_by(Condition, Protein_Index) %>%
#   summarise(max(Score))
# 
# colnames(map_of_NEP) = c("Condition", "Index", "Site_Score")
# 
# score_list = c(2, 3, 4, 5, 6, 7, 9)
# 
# x = ggplot(data = map_of_NEP, mapping = aes(x = Condition, 
#                                               y = Index, 
#                                               fill = Site_Score)) +
# geom_tile() +
#   theme_classic() +
#   xlab(label = "Condition") +
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20),
#         axis.text.y = element_text(size = 20),
#         plot.title = element_text(hjust = 0.7, size = 35),
#         axis.title = element_text(size = 25),
#         legend.title = element_text(size = 20),
#         legend.text = element_text(size = 15)) +
#   scale_fill_viridis(name = "Max Site Score", breaks = score_list, labels = c("2", "3", "4", "5", "6", "7", "9"), direction = -1, option = "D") +
#   ggtitle(label = "Sites on Nuclear Export Protein") 
# 
# ggsave("isabel_NEP_sites.svg", x, width = 30, height = 20, units = "cm")
```